%!TEX root = main.tex
\documentclass[main.tex]{subfiles}

\begin{document}
\section{Survey}\label{sec:appendix-survey}
\begin{enumerate}
	\item Is the information of each page clear?
	\item Is the message easy to read?
	\item Does the colouring add to, or take away, from the message?
	\item Is the Welcome message clear?
	\item Is the Goodbye message clear?
	\item Does this discourage you from making a call?
\end{enumerate}
\section{Call Transcripts}\label{sec:appendix-transcripts}
\subsection{Youtube Videos}
\begin{enumerate}
	\item From \url{https://www.youtube.com/watch?v=1UE_Q1pprEg}, retrieved Jun 15, 2017.
	\begin{quote}
		Hello, my name is Shane. We are the online service provider regarding every[sic] each and every Windows Operating computer okay. There are malicious files that are downloading in your computer okay they are not very safe for your computer.
	\end{quote}

	\item From \url{https://www.youtube.com/watch?v=XY0RUCCBPik}, retrieved Jun 15, 2017.
	\begin{quote}
		\textbf{Caller:} My name is Alina okay calling you from Talktalk Internet Service Centre, your Internet Service Provider okay.\\
		\textbf{User:} Okay, yes what can I do for you?\\
		\textbf{Caller:} The reason why I gave you a call today okay
	\end{quote}

	\item From \url{https://www.youtube.com/watch?v=0aJ12CiQh1M}, retrieved Jun 15, 2017.
	\begin{quote}
		\textbf{Caller:} Calling from Windows sir, technical department.\\
		\textbf{User:} Oh yes.\\
		\textbf{Caller:} The system you are using for your computer.\\
		\textbf{User:} Yes windows.
	\end{quote}
\end{enumerate}

\subsection{From A Website}

\section{Scripts}\label{sec:appendix-scripts}
All scripts, code segments, website templates, and testing versions, along with the copies of the raw \LaTeX{} data are found on the Github repository at:
\\\\
\url{https://www.github.com/mengkiangseah/fyp}

\end{document}
